\documentclass[a4paper,10pt, onecolumn]{article}

\usepackage{multicol}
\usepackage{color}

\usepackage{comment}
 
\setlength{\columnseprule}{0.7pt}
\setlength\columnsep{60pt}
\def\columnseprulecolor{\color{black}}
 
\begin{document}

   \centerline{\underline{\emph{\huge Risotto}}}
   \vspace{0.5cm}

\begin{multicols}{2}



\section*{Ingredients}

\begin{itemize}
% List Ingredients here
\item 100g Risotto Rice Per Person.
\item Box of Pancetta Cubes.
\item 1 Box of Mushrooms.
\item Piquante Peppers.
\item Bag of Rocket.
\item Parmesan Cheese or Grated Cheese.
\item Chicken OXO Cube.
\item Olive Oil.
\item White Wine.
\item Salt and Pepper.
\end{itemize}

\columnbreak

\section*{Tools}
\begin{itemize}
% List Utensils here
\item Deep Frying Pan.
\item Pint Sized Measuring Jug.
\item Kettle.
\end{itemize}

\end{multicols}
\hrulefill
\section*{Method}

\begin{enumerate}
% List Steps here
\item Heat a slug of olive oil at a medium heat in frying pan (~40\%).
\item Add the pancetta cubes and fry for a bit.
\item Then add risotto rice and make sure that all of the rice is covered in the oil.
\item Whilst the pancetta and rice is frying wash and quarter mushrooms and cut piquante peppers.
\item Turn down heat (to 25\%), the add 1 glug of wine and $\frac{1}{4}$ pint of stock.
\item Add mushrooms and peppers.
\item Season with salt and pepper.
\item Add lid, turn up heat untill boiling then turn down to simmer.
\item If risotto is moist and bubbling then it is ok, if it is dry then need to add more stock.
\item Taste rice, if soft then ready to go, if not wait or add more stock. Should take ~30 mins.
\item Stir in cheese and rocket at the end and serve.
\end{enumerate}
 

\end{document}
